Near Optimal Behavior with Approximate Abstraction

### 2016-02-04 paper/example_domains.tex

NChain, pictured in Figure~\ref{fig:nchain-visual}, is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}. In all states, the agent has two actions available: advance down the chain, or return to state 0. The agent receives a small positive reward, $r_{small}$ for returning to state 0, and no reward for advancing down the chain, unless the agent transitions to the last state in the chain. This transition provides a large positive reward, $r_{large}$. Thus, the agent must explore down the chain and avoid the intermediate smaller rewards in order to find the large reward at the end. Transitions also have small slip probability such that the applied action has the unintended effect of the opposing action (so advancing down the chain with probability $\rho$ will take the agent back to state 0, and vice versa). In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.

>>>>

NChain, pictured in Figure~\ref{fig:nchain-visual}, is a simple MDP heavily investigated in the Bayesian Reinforcement Learning literature due to the interesting exploration problem it poses~\cite{dearden1998bayesian}. In all states, the agent has two actions available: advance down the chain, or return to state 0. The agent receives a small positive reward, $r_{small}$ for returning to state 0, and no reward for advancing down the chain, unless the agent transitions to the last state in the chain. This transition provides a large positive reward, $r_{large}$. Transitions also have small slip probability, $\rho$, such that the applied action results in the wrong action.g In our implementation, we set $N=10$, $\rho=0.2$, $r_{small} = 0.2$, and $r_{large} = 1.0$.
